NumPy---Array Computation for Python

### 2020-01-07 body.tex
Add notes
Start rewriting Recent Development section

\section*{Hybrid development}

@@

In 2018, we hired our first full-time developers ...

The first activities organized for the new grants were a development planning
sprint, a weekly community call, and a meeting to write a draft roadmap.
Since the roadmap was meant to represent community consensus on future
development, it was presented for comment at the annual SciPy
conference during a so-called ``Birds of a Feather'' session, attended
by more than 100 people.  One additional meeting was held to discuss
specific enhancements, such as the development of a new data-type
system.  The final roadmap was vetted by the community via online
discussion before being accepted.

>>>>

\section*{Recent development}

@@

The project entered a new phase of development in 2018 with the hiring of two full-time developers.  With this new resource, we were able to address long-outstanding technical debt, review more volunteer work, and implement several larger features.

In an open source project that has relied on volunteer effort for so many years, the introduction of paid work can be disruptive. In such communities, decision making power is often tied to contributed effort, and when some individuals are paid it skews the equation. To guard against this, the project set up an explicit governance structure, formalized the feature proposal process, and constructed a development roadmap with extensive feedback from the community.   Individuals were hired that were already active in NumPy and its surrounding communities, who already shared the project's norms and values.  Funded developers were also expected to review code as a part of their job, thereby supporting the work done by volunteers.

Still, funded development allowed for the implementation of several larger features, which require a sizeable amount of time, conversations with multiple stakeholders, and longer term focus; and were therefore more difficult to accomplish by volunteer effort alone.

% --- I'm here now ---
